Appendix A

### 2020-10-04 appendixA/appendixA.Rmd
changing density figures

# Here, we are taking our tracking data and removing mpm (meters moved per minute) that are equal to zero, since these won't allow for distributio fittings. We also create a new variable for Bird ID, and modify net squared displacement. 
df <- ptpl %>%
  dplyr::filter(mpm != 0) %>%
  ungroup() %>%
  mutate(Bird_ID = paste0("B", Bird_ID),
         sqR2n = sqrt(R2n)) %>% 
  group_by_("id", "burst") %>% 
  mutate(cumdt = cumsum(dt)/60) %>% 
  ungroup()

dist.used <- c( "exp", "gamma", "weibull", "lnorm")

param <- c("rate", "shape", "rate", "shape", "scale", "meanlog", "sdlog")
dist <- c("exp", "gamma", "gamma", "weibull", "weibull", "lnorm", "lnorm")

@@

```{r fig.width=10}
pop_dens_plot <- df %>%
  ggplot(., aes(x = mpm)) +
  geom_line(stat = "density", color = "grey", lwd = 1) +
  #geom_line(aes(x = dist, group = id), stat = "density", alpha = 0.4) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  ylim(0, 0.05) +
  labs(title = "Population") +
  theme_classic()

ind_dens_plot <- df %>%
  ggplot(., aes(x = mpm)) +
  #geom_line(stat = "density", color = "red", lwd = 1) +
  geom_line(aes(x = mpm, group = id), stat = "density", alpha = 0.4) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  ylim(0, 0.05) +
  labs(title = "Individual") +
  theme_classic()

fam_dens_plot <- df %>%
  filter(., fam_g != "unknown") %>% 
  ggplot(., aes(x = mpm)) +
  #geom_line(stat = "density", color = "red", lwd = 1) +
  geom_line(aes(x = mpm, group = fam_g), stat = "density", alpha = 0.4) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  ylim(0, 0.05) +
  labs(title = "Family") +
  theme_classic()

ggarrange(pop_dens_plot, ind_dens_plot, fam_dens_plot, ncol = 3)

>>>>

# Here, we are taking our tracking data and removing mpm (meters moved per minute) that are equal to zero, since these won't allow for distribution fittings. We also create a new variable for Bird ID, and modify net squared displacement. 
df <- ptpl %>%
  dplyr::filter(mpm != 0) %>%
  ungroup() %>%
  mutate(Bird_ID = paste0("B", Bird_ID)) %>% 
  group_by_("id", "burst") %>% 
  mutate(cumdt = cumsum(dt)/60) %>% 
  ungroup()

# These are the distributions I am considering for characterizing the meters moved per minute in the data
dist.used <- c( "exp", "gamma", "weibull", "lnorm")

# These are the parameters and associated distributions that will be needed later to build a dataframe of parameters
param <- c("rate", "shape", "rate", "shape", "scale", "meanlog", "sdlog")
dist <- c("exp", "gamma", "gamma", "weibull", "weibull", "lnorm", "lnorm")

@@

Density plots showing variation in biological classification levels, where the red line shows the density plot for what we consider the population (all the data together), and grey lines show individuals (left) or family groups (right).

```{r fig.width=12, fig.height=5}
ind_dens_plot <- df %>%
  ggplot(., aes(x = mpm)) +
  geom_line(stat = "density", color = "red", lwd = 1) +
  geom_line(aes(x = mpm, group = id), stat = "density", alpha = 0.4) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  ylim(0, 0.055) +
  labs(title = "Individual") +
  theme_classic()

fam_dens_plot <- df %>%
  filter(., fam_g != "unknown") %>% 
  ggplot(., aes(x = mpm)) +
  geom_line(stat = "density", color = "red", lwd = 1) +
  geom_line(aes(x = mpm, group = fam_g), stat = "density", alpha = 0.4) +
  geom_vline(xintercept = 0, color = "grey") +
  geom_hline(yintercept = 0, color = "grey") +
  ylim(0, 0.055) +
  labs(title = "Family") +
  theme_classic()

ggarrange(ind_dens_plot, fam_dens_plot)
